---
title: "Support tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# SUPPORT TABLE

*Additional tables will be appended instead. Refer go to: Update table*

This table will hold information that cuts across all countries. It will be used for dynamically updating UI elements of the tool. 

This table will contain, for each country:
* Products under each country
* Ownership of customers

## Packages

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(DBI)
library(tidyverse)
```


## Ownership information

```{r}
ke_ownership <- readRDS(file = "../../../Data Prep/KE/03. Extract additional customer details/outputs/ke_recommendations_detailed.rds") %>%
  ungroup() %>%
  distinct(ownership) %>%
  pull(ownership)

zw_ownership <- readRDS(file = "../outputs/zw_recommendations_detailed.rds") %>%
  ungroup() %>%
  distinct(ownership) %>%
  pull(ownership)

ug_ownership <- readRDS(file = "../../UG/outputs/ug_recommendations_detailed.rds") %>% 
  ungroup() %>% 
  distinct(ownership) %>% 
  pull(ownership)

ke_ownership
zw_ownership
ug_ownership
```

```{r}
supp_sqlite_path_ug <- "../../../App/uap_cross_sell/db/support_tayo.db"
con_supp_ug <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path_ug)

ug_ownership <-
tbl(src = con_supp_ug, "support") %>% 
  filter(country=="Uganda") %>% 
  filter(!is.na(ownership)) %>% 
  pull(ownership)

ug_ownership
```


## Product information


```{r}
ke_products <- readRDS(file = "../../../Data Prep/KE/02. Create rating matrices/outputs/products_rating_matrix.rds") %>%
  colnames()

zw_products <- readRDS(file = "../../../Data Prep/ZW/02. Create rating matrices/outputs/products_rating_matrix.rds") %>%
  colnames()

ug_products <- readRDS(file = "../../../Data Prep/UG/02. Create rating matrices/outputs/products_rating_matrix.rds") %>% 
  colnames()

length(ke_products)
length(zw_products)
length(ug_products)
```


```{r}
support_df <-
rbind(
  tibble(
    country = "Zimbabwe",
    products = zw_products,
    ownership = c(zw_ownership,
                  rep(NA, times = length(zw_products) - length(zw_ownership))
                  )
    ),
  
  tibble(
    country = "Kenya",
    products = ke_products,
    ownership = c(ke_ownership,
                  rep(NA, times = length(ke_products) - length(ke_ownership))
                  )
    )
  )

support_df
```


```{r}
ug_tibble <- tibble(
    country = "Uganda",
    products = ug_products,
    ownership = c(ug_ownership,
                  rep(NA, times = length(ug_products) - length(ug_ownership))
                  )
    )

ug_tibble
```


## Save into db

```{r}
supp_sqlite_path <- "../../../App/uap_cross_sell/db/support.db"
con_supp <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path)
```


```{r}
copy_to(dest = con_supp, 
        df = support_df, 
        name = "support", 
        overwrite = TRUE, 
        temporary = FALSE)
```


# Update table

## db Connection

```{r}
supp_sqlite_path <- "../../../App/uap_cross_sell/db/support.db"

con_supp <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path)

dbListTables(conn = con_supp)
```

## GH Update

### Product information

```{r}
gh_products <-
readRDS(file = "../../../Data Prep/GH/product_holding/products_rating_matrix.rds") %>% 
  colnames()

gh_products
```

### Ownership information

```{r}
gh_ownership <-
readRDS(file = "../gh_recommendations_detailed.rds") %>% 
  ungroup() %>% 
  distinct(ownership) %>% 
  pull(ownership)

gh_ownership
```

### Dataframe

```{r}
gh_tibble <-
tibble(country = "Ghana",
       products = gh_products,
       ownership =c(gh_ownership, 
                    rep(x = NA, 
                        times = length(gh_products) - length(gh_ownership))
                    )
       )

gh_tibble
```

## Save to db

```{r}
dbWriteTable(con = con_supp, "support", gh_tibble, append=TRUE, row.names = FALSE)
```


# Sense check

```{r}
dbListTables(conn = con_supp)

dim(gh_tibble)

tbl(src = con_supp, "support") %>% 
  filter(country=="Ghana") %>% 
  collect() %>% 
  dim()
```

