---
title: "Customer details"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PACKAGES

```{r message=FALSE, warning=FALSE}
library(recommenderlab)
library(glue)
library(data.table)
library(readxl)
library(tidyverse)
```

# CUSTOMER DETAILS

In this markdown we want to match `ACCOUNT_NO` in the `products_rating_matrix.rds` to customer details:
* Customer name
* Contact details
* Products held
* Tenure
* Intermediary Code

### Customer attributes

The following attributes will be required from the customer master files.

```{r}
c("ACCOUNT_NO",
  "PRODUCT",
  "TITLE",
  "FULL_NAMES",
  "TELEPHONE_NUMBER",
  "MOBILE_NUMBER",
  "GENDER",
  "PRIMARY_EMAIL",
  "POSTAL_ADDRESS",
  "POSTAL_CODE",
  "POSTAL_CITY") -> customer_attributes
```

## Product info

Product business lines

```{r}
product_businesslines <- readRDS(file = "../../Models/KE/product_businesslines.rds")

product_businesslines
```

Account Numbers tied to products

```{r}
products_rating_matrix <- readRDS("./product_holding/products_rating_matrix.rds")

customer_products <- as(products_rating_matrix, "data.frame") %>% 
  rename(ACCOUNT_NO = user,
         PRODUCT = item) %>% 
  left_join(product_businesslines, by = "PRODUCT")

customer_products
```

# ASSET MGT

## Asset mgt accounts


```{r}
asset_mgt_accounts <- 
customer_products %>%
  filter(BUSINESS_LINE == "Asset")

head(asset_mgt_accounts)
```

## Accounts <=> Products

```{r}
asset_product_info <-
asset_mgt_accounts %>% 
  group_by(ACCOUNT_NO) %>% 
  mutate(product_count = n_distinct(PRODUCT),
         products = paste0(PRODUCT, collapse = ", ")) %>% 
  select(ACCOUNT_NO, products, product_count) %>% 
  slice(1)

head(asset_product_info)
```

Asset Management data

```{r}
# Customer name, contact details
asset_customer_master <- read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/asset_mgt/Customer Dataset.csv")

# Products held
products_rating_matrix

# Tenure
# No information on joining date

# Intermediary code
asset_agents_master <- read_csv("../../../../C - Documentation/Data/festus_extraction/kenya/asset_mgt/Agent Dataset.csv")
```


## Accounts <=> Customer Details

```{r}
head(asset_customer_master)
```


Check number of records in common in the two files.

```{r}
length(intersect(x = asset_mgt_accounts$ACCOUNT_NO, 
                 y = asset_customer_master$ACCOUNT_NO))
```


```{r}
asset_customer_info <-
asset_mgt_accounts %>% 
  left_join(asset_customer_master, by = "ACCOUNT_NO") %>% 
  select(all_of(customer_attributes)) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE) %>% 
  select(-PRODUCT)

dim(asset_customer_info)
head(asset_customer_info)
```


## Accounts <=> Agent

```{r}
asset_acc_intermediary <- read_csv("../../../../C - Documentation/Data/festus_extraction/kenya/asset_mgt/Investment Account Dataset.csv") %>% 
  mutate(ACCOUNT_NO = as.character(ACCOUNT_NO))

head(asset_acc_intermediary)
```


```{r}
asset_agent_info <-
asset_acc_intermediary %>% 
  select(ACCOUNT_NO,INTERMEDIARY_CODE) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

head(asset_agent_info)
```


## Asset customer details


```{r}
asset_customer_details <-
asset_mgt_accounts %>%
  left_join(asset_customer_info, by = "ACCOUNT_NO") %>%
  left_join(asset_agent_info, by = "ACCOUNT_NO") %>% 
  left_join(asset_product_info, by = "ACCOUNT_NO") %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

dim(asset_customer_details)
head(asset_customer_details)
```

## Intermediated

```{r}
asset_customer_details <-
asset_customer_details %>% 
  mutate(intermediated = if_else(condition = !is.na(INTERMEDIARY_CODE),
                                 true = "Yes",
                                 false = "No"))

head(asset_customer_details)
```


## Sense check

We want to see one Account Number and all it's products and customer details under it.

```{r}
asset_customer_details %>% 
  count(ACCOUNT_NO, sort = TRUE)
```


## Convert to single column

```{r}
#TODO: An account could be sharing products across business lines so this should come together with account ownership

asset_customer_details_final <-
asset_customer_details %>% 
  mutate(customer_details = glue("Names:{FULL_NAMES}
                                 Agent Code:{INTERMEDIARY_CODE}
                                 Product Holding:{product_count}
                                 Current Products:{products}
                                 Tel No:{TELEPHONE_NUMBER}
                                 Email:{PRIMARY_EMAIL}", 
                                 .na = "Not Found")) %>% 
  select(ACCOUNT_NO, intermediated, customer_details)


dim(asset_customer_details_final)
head(asset_customer_details_final)
```


# HEALTH INSURANCE

## Health insurance accounts

Health product holding.

```{r}
health_accounts <-
customer_products %>%
  filter(BUSINESS_LINE == "Health")

head(health_accounts)
```

## Accounts <=> Products

```{r}
health_product_info <-
health_accounts %>%
  select(ACCOUNT_NO, PRODUCT) %>% 
  group_by(ACCOUNT_NO) %>% 
  mutate(product_count = n_distinct(ACCOUNT_NO),
         products = paste0(PRODUCT, collapse = ", ")) %>% 
  slice(1) %>% 
  select(-PRODUCT)

head(health_product_info)
```

## Accounts <=> Customer details

Health customer master file.

```{r}
health_customers <- vroom::vroom("../../../../C - Documentation/Data/festus_extraction/kenya/health/health_customer_kenya.csv")
```

Health insurance products.

```{r}
health_acc_products <- vroom::vroom("../../../../C - Documentation/Data/festus_extraction/kenya/health/policyheader_nonlife_kenya_product_names-HEALTH.csv") %>% 
  select(ACCOUNT_NO,MEMBER_NO)
```

The `PRI_ACCOUNT_NO` in the customer master file should be joined to the `MEMBER_NO` in the file containing health insurance products.

```{r}
head(health_customers)
```

Check how many records are common in the two files.

```{r}
length(intersect(x = health_acc_products$MEMBER_NO, 
                 y = health_customers$PRI_ACCOUNT_NO))
```

Match customer details to product information.

```{r}
health_customer_info <-
health_acc_products %>% 
  left_join(health_customers, by = c("MEMBER_NO"="PRI_ACCOUNT_NO")) %>% 
  rename(ACCOUNT_NO = ACCOUNT_NO.x) %>% 
  select(any_of(x = customer_attributes)) %>% 
  mutate(ACCOUNT_NO = as.character(ACCOUNT_NO))%>% 
  group_by(ACCOUNT_NO) %>% 
  slice(1) %>% 
  ungroup()

dim(health_customer_info)
head(health_customer_info)
```


## Accounts <=> Agent

This file links Account Numbers to Intermediary Codes

```{r}
health_agents <- vroom::vroom(file = "../../../../C - Documentation/Data/festus_extraction/kenya/health/policydetails_health_kenya.csv") %>% 
  select(ACCOUNT_NO, AGENT_CODE) %>% 
  mutate(ACCOUNT_NO = as.character(ACCOUNT_NO))
```

We check if we can join this file to the main Product Account file.

```{r}
length(intersect(x = health_accounts$ACCOUNT_NO, 
                 y = health_agents$ACCOUNT_NO))
```

Join Health Account to Agents

```{r}
health_agent_info <-
health_accounts %>% 
  left_join(health_agents) %>% 
  select(ACCOUNT_NO, AGENT_CODE) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

head(health_agent_info)
```

## Health customer details

```{r}
health_customer_details <-
health_accounts %>% 
  select(ACCOUNT_NO) %>% 
  # Add Agent code
  left_join(health_agent_info, by = "ACCOUNT_NO") %>% 
  # Add Product info
  left_join(health_product_info, by = "ACCOUNT_NO") %>% 
  # Add Customer info
  left_join(health_customer_info, by = "ACCOUNT_NO")

dim(health_customer_details)
head(health_customer_details)
```
## Intermediated

```{r}
health_customer_details <-
health_customer_details %>% 
  mutate(intermediated = if_else(condition = !is.na(AGENT_CODE),
                                 true = "Yes",
                                 false = "No"))

head(health_customer_details)
```


## Single column

```{r}
health_customer_details_final <-
health_customer_details %>% 
  mutate(customer_details = glue("Names:{FULL_NAMES}
                                 Agent Code:{AGENT_CODE}
                                 Product Holding:{product_count}
                                 Current Product:{products}
                                 Tel No:{TELEPHONE_NUMBER}
                                 Email:{PRIMARY_EMAIL}", 
                                 .na = "Not Found")) %>% 
  select(ACCOUNT_NO, intermediated, customer_details) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

dim(health_customer_details_final)
head(health_customer_details_final)
```
Sense check

```{r}
health_customer_details_final %>% 
  count(ACCOUNT_NO, sort = TRUE)


health_customer_details_final %>% 
  filter(ACCOUNT_NO=="420754")
```

# LIFE INSURANCE

## Accounts <=> Products

```{r}
life_accounts <-
customer_products %>% 
  filter(BUSINESS_LINE=="Life")

life_accounts
```


Import customer details from the customer master file.

## Accounts <=> Customer

```{r}
life_customer_master <-
read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/life/new/Kenya Life Customers.csv")

life_customer_master
```

Number of accounts that cannot be joined to the customer master.

```{r}
length(setdiff(x = life_accounts$ACCOUNT_NO, 
               y = life_customer_master$ACCOUNT_NO))
```


```{r}
life_customer_info <-
life_accounts %>% 
  left_join(life_customer_master, by = "ACCOUNT_NO") %>% 
  select(all_of(customer_attributes)) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

life_customer_info
```

## Accounts <=> Agents

Agent IDs for each Account Number

```{r}
life_agents_info <-
read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/life/new/Kenya Life Policies and Policy Details.csv") %>% 
  select(ACCOUNT_NO, AGENT_CONTRACT_ID) %>% 
  distinct(ACCOUNT_NO, AGENT_CONTRACT_ID) %>% 
  mutate(intermediated = if_else(condition = !is.na(AGENT_CONTRACT_ID),
                                 true = "Yes",
                                 false = "No"))

life_agents_info
```

## Life customer details

We want one record of customer details for each customer Account Number.

```{r}
life_customer_details <-
life_accounts %>% 
  left_join(life_agents_info, by = "ACCOUNT_NO") %>% 
  left_join(life_customer_info) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

life_customer_details
```

# GENERAL INSURANCE

## Accounts <=> Products

```{r}
gi_accounts <-
customer_products %>% 
  filter(BUSINESS_LINE=="General")

gi_accounts
```

## Accounts <=> Agents

```{r}
gi_products_raw <- readRDS(file = "./gi_products_raw.rds")

gi_agent_info <-
gi_products_raw %>% 
  select(ACCOUNT_NO, INTERMEDIARY_CODE) %>% 
  filter(!is.na(ACCOUNT_NO)) %>% 
  mutate(intermediated = if_else(condition = !is.na(INTERMEDIARY_CODE),
                                 true = "Yes",
                                 false = "No")) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

gi_agent_info
```

## Accounts <=> Customers

Number of account that match between gi_accounts and gi_clients_raw

```{r}
length(intersect(x = gi_accounts$ACCOUNT_NO, y = gi_clients_raw$ACCOUNT_NO))
```

```{r}
gi_clients_raw <- readRDS(file = "./gi_clients_raw.rds")

gi_customer_info <-
gi_clients_raw %>% 
  select(any_of(customer_attributes))

gi_customer_info
```

## Customer details

Merge customer and agents information to GI accounts. At the end we want one record per customer account containing all customer details.

```{r}
gi_customer_details <-
gi_accounts %>% 
  select(ACCOUNT_NO) %>% 
  left_join(gi_agent_info, by = "ACCOUNT_NO") %>% 
  left_join(gi_customer_info, by = "ACCOUNT_NO") %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

dim(gi_customer_details)
gi_customer_details
```


# PRODUCT VALUES

## Asset Management

Customer statements contains the value of new business.

```{r}
asset_statement <- read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/asset_mgt/Investment Account Statement Dataset.csv")

asset_statement_accounts <- read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/asset_mgt/Investment Account Dataset.csv") %>% 
              select(ACCOUNT_NO, CUSTOMER_NUMBER, FUND_NAME)
```

### Transactions to exclude

From this analysis, we filter out:
* `TRANSACTION_AMOUNT` < 0
* `Cancellation`
* `Purchase` (these are re-investments)
* `Temporary Purchase`

```{r}
asset_statement %>% 
  filter(TRANSACTION_AMOUNT>0) %>% 
  distinct(TRANSACTION_TYPE)
```

### Value by Transaction Type

Average value of transaction types.

```{r}
asset_statement %>% 
  select(TRANSACTION_TYPE, TRANSACTION_AMOUNT) %>% 
  filter(TRANSACTION_AMOUNT > 0) %>% 
  filter(TRANSACTION_TYPE != "Cancellation") %>% 
  filter(TRANSACTION_TYPE != "Purchase") %>%
  group_by(TRANSACTION_TYPE) %>% 
  summarise(avg = mean(TRANSACTION_AMOUNT),
            accounts = n()) %>% 
  mutate(gross_avg = mean(avg),
         customers = sum(accounts))
```
### Value by Product

Values of different asset management products.

```{r}
dim(asset_statement)

asset_product_values_raw <-
asset_statement %>% 
  filter(TRANSACTION_AMOUNT > 0) %>% 
  filter(!TRANSACTION_TYPE %in% c("Purchase","Cancellation","Temporary Purchase")) %>% 
  select(CUSTOMER_NUMBER, CUSTOMER_ACCOUNT_NO, 
         TRANSACTION_TYPE, TRANSACTION_AMOUNT) %>% 
  left_join(asset_statement_accounts, 
            by = c("CUSTOMER_NUMBER"="ACCOUNT_NO")) %>% 
  left_join(asset_statement_accounts,
            by = c("CUSTOMER_ACCOUNT_NO"="CUSTOMER_NUMBER")) %>% 
  left_join(asset_statement_accounts,
            by = c("CUSTOMER_ACCOUNT_NO"="ACCOUNT_NO")) %>%
  mutate(FUND_NAME = coalesce(FUND_NAME, FUND_NAME.x)) %>% 
  select(CUSTOMER_NUMBER_stmt = CUSTOMER_NUMBER.x, 
         CUSTOMER_ACCOUNT_NO, TRANSACTION_TYPE, TRANSACTION_AMOUNT, 
         CUSTOMER_NUMBER_acc = CUSTOMER_NUMBER.y, 
         ACCOUNT_NO, FUND_NAME)

asset_product_values_raw %>% 
  filter(is.na(FUND_NAME))
```

```{r}
asset_product_values_proc <-
asset_product_values_raw %>% 
  group_by(FUND_NAME) %>% 
  summarise(product_value = mean(TRANSACTION_AMOUNT),
            accounts = n()) %>% 
  rename(PRODUCT = FUND_NAME)

asset_product_values_proc
```

### Missing products

```{r}
asset_product_values_final <-
asset_mgt_accounts %>% 
  distinct(PRODUCT) %>% 
  left_join(asset_product_values_proc) %>%
  replace_na(replace = list(product_value = mean(.$product_value, na.rm = TRUE)))

asset_product_values_final
```


## Health Insurance

```{r}
health_statement <-
  read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/health/Health Policy Statement Kenya.csv") %>% 
  select(POLICY_NO, RECEIPT_AMOUNT)

health_statement_accounts <-
  vroom::vroom(file = "../../../../C - Documentation/Data/festus_extraction/kenya/health/policyheader_nonlife_kenya_product_names-HEALTH.csv", ) %>% 
  select(POLICY_NO, ACCOUNT_NO, MEMBER_NO) %>% 
  mutate(ACCOUNT_NO = as.character(ACCOUNT_NO))
```

### Transactions to exclude

To exclude records where:
* `RECEIPT_AMOUNT` < 0

```{r}
dim(health_statement)

health_statement %>% 
  filter(RECEIPT_AMOUNT < 0)
```

### Add Account Numbers

Add Account Numbers to statement.

```{r}
health_statement_refs <-
health_statement %>% 
  extract(col = POLICY_NO, 
          into = c("policy","ref"), 
          regex = "(^.*)/(.*)", 
          remove = FALSE, 
          convert = FALSE)

head(health_statement_refs)
```

```{r}
health_statement_accounts_refs <-
health_statement_accounts %>% 
  filter(POLICY_NO != "NULL") %>% 
  extract(col = POLICY_NO,
          into = c("policy_1","ref"),
          regex = ".*/([[:alnum:]]+)/([0-9]{2}$)",
          remove = FALSE, 
          convert = FALSE) %>% 
  extract(col = POLICY_NO,
          into = c("policy_2"),
          regex = "([[:alnum:]]+)/[0-9]{2}",
          remove = FALSE,
          convert = FALSE) %>% 
  mutate(policy = coalesce(policy_1, policy_2)) %>% 
  select(-policy_1, -policy_2)

health_statement_accounts_refs %>% 
  filter(is.na(policy))

dim(health_statement_accounts_refs)
head(health_statement_accounts_refs)
```

Check how many of the two records can be merged

```{r}
#TODO: Consult Keldine on improving the matching of the two files

length(unique(health_statement_refs$policy))

length(intersect(x = health_statement_refs$policy,
                 y = health_statement_accounts_refs$policy))

length(setdiff(x = health_statement_refs$policy,
               y = health_statement_accounts_refs$policy))

setdiff(x = health_statement_refs$policy,
        y = health_statement_accounts_refs$policy)[1:10]
```

### Add Product Names

Add the cleaned Product Names associated with the Account Numbers.

```{r}
health_product_values_raw <-
health_statement_refs %>% 
  inner_join(health_statement_accounts_refs, by = "policy") %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE) %>% 
  left_join(health_accounts, by = "ACCOUNT_NO")

dim(health_product_values_raw)
head(health_product_values_raw)
```

### Value by Product

```{r}
health_product_values_proc <-
health_product_values_raw %>% 
  group_by(PRODUCT) %>% 
  summarise(product_value = mean(RECEIPT_AMOUNT),
            accounts = n())

health_product_values_proc
```

### Missing products

```{r}
health_product_values_final <-
health_accounts %>% 
  distinct(PRODUCT) %>% 
  left_join(health_product_values_proc, by = "PRODUCT") %>% 
  replace_na(replace = list(product_value = mean(.$product_value, na.rm = TRUE)))

health_product_values_final
```

## Life Insurance

### Transactions

Life insurance account statements.

```{r}
life_statements <-
read_csv("../../../../C - Documentation/Data/festus_extraction/kenya/life/new/Kenya Life Policy Statements.csv") %>% 
  select(CONTRACT_ID, PAYMENT_PAID) %>% 
  filter(PAYMENT_PAID > 0)

life_statements
```

### Add Products

First add Accounts

```{r}
life_statements_accounts <-
  read_csv(file = "../../../../C - Documentation/Data/festus_extraction/kenya/life/new/Kenya Life Policies and Policy Details.csv") %>% 
  select(CONTRACT_ID, ACCOUNT_NO)

life_statements_accounts
```

Check for duplicates

```{r}
any(duplicated(life_statements_accounts))
```

### Value by Product

Then add product names.

```{r}
life_product_values <-
life_statements %>% 
  left_join(life_statements_accounts, by = "CONTRACT_ID") %>% 
  left_join(life_accounts, by = "ACCOUNT_NO") %>% 
  group_by(PRODUCT) %>% 
  summarise(product_value = mean(PAYMENT_PAID),
            accounts = n()) %>% 
  right_join(life_accounts %>% distinct(PRODUCT))

life_product_values
```

## General Insurance

Import policy statements. Since these have transaction dates, we can limit ourselves to the most recent transactions over the last 3 years. These appear in `gi_policy_statement_kenya_4.xls`.

10 worksheets. Read everything as text.

### Policy Statements

```{r}
gi_statement_1 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 1, col_types = "text")

gi_statement_2 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 2, col_types = "text")

gi_statement_3 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 3, col_types = "text")

gi_statement_4 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 4, col_types = "text")

gi_statement_5 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 5, col_types = "text")

gi_statement_6 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 6, col_types = "text")

gi_statement_7 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 7, col_types = "text")

gi_statement_8 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 8, col_types = "text")

gi_statement_9 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 9, col_types = "text")

gi_statement_10 <-
read_excel(path = "../../../../C - Documentation/Data/festus_extraction/kenya/general/gi_policy_statement_kenya_4.xls", sheet = 10, col_types = "text")
```


```{r}
gi_statement_raw <- bind_rows(gi_statement_1, gi_statement_2, gi_statement_3, gi_statement_4, gi_statement_5, gi_statement_6, gi_statement_7, gi_statement_8, gi_statement_9, gi_statement_10) %>% 
  select(POLICY_NO, AMOUNT) %>%
  filter(AMOUNT > 0) %>% 
  filter(!is.na(POLICY_NO))

gi_statement_raw
```

```{r}
rm(gi_statement_1, gi_statement_2, gi_statement_3, gi_statement_4, gi_statement_5, gi_statement_6, gi_statement_7, gi_statement_8, gi_statement_9, gi_statement_10)
```


### Add Product Names

Number of matching records.

```{r}
length(unique(gi_statement_raw$POLICY_NO))

length(intersect(x = gi_statement_raw$POLICY_NO, y = gi_products_raw$POLICY_NO))
```


```{r}
gi_product_values <-
gi_statement_raw %>% 
  left_join(gi_products_raw %>% 
              select(POLICY_NO, POLICY_TYPE), 
            by = "POLICY_NO") %>% 
  mutate(AMOUNT = as.numeric(AMOUNT)) %>% 
  group_by(POLICY_TYPE) %>% 
  summarise(product_value = mean(AMOUNT),
            accounts = n()) %>% 
  rename(PRODUCT = POLICY_TYPE)

gi_product_values
```

## Merge all products

```{r}
product_values <-
bind_rows(asset_product_values_final,
          health_product_values_final,
          life_product_values,
          gi_product_values) %>% 
  mutate(product_value = round(product_value)) %>% 
  filter(!is.na(PRODUCT))

product_values
```


# PRODUCT & OWNERSHIP

This portion needs to come last so that we can have a full view of all the business lines to which an individual customer account belongs to and products they hold.

## Product Holding & Account Ownership


```{r}
account_info <-
bind_rows(asset_mgt_accounts,
          health_accounts,
          life_accounts,
          gi_accounts) %>% 
  distinct(ACCOUNT_NO, PRODUCT, BUSINESS_LINE) %>% 
  group_by(ACCOUNT_NO) %>% 
  add_count(ACCOUNT_NO, name = "product_count") %>% 
  mutate(products = paste0(PRODUCT, collapse = ", "),
         ownership = paste0(unique(BUSINESS_LINE), collapse = ", ")) %>%
  slice(1) %>% 
  select(ACCOUNT_NO, ownership, product_count, products)

dim(account_info)
View(account_info)
```

## Test

```{r}
account_info %>% filter(ACCOUNT_NO %in% c("10867","1610"))
```

# ALL CUSTOMERS INFO

Create a new single column. We need to replace `products` and `product_count` with the new `account_info`

Merge customer details and product information.

## Customer details

Retail purely customer information.

```{r}
life_customer_details_final <-
life_customer_details %>% 
  select(-PRODUCT, -BUSINESS_LINE, -rating)

asset_customer_details_final <-
asset_customer_details %>% 
  select(-products, -product_count, -PRODUCT, -BUSINESS_LINE, -rating)

health_customer_details_final <-
health_customer_details %>% 
  select(-products, -product_count)

gi_customer_details
```


## Product details

```{r}
account_info
```

## Merge customer details

```{r}
customer_details_proc <-
rbind(life_customer_details_final %>% 
        rename(INTERMEDIARY_CODE = AGENT_CONTRACT_ID),
      asset_customer_details_final,
      health_customer_details_final %>% 
        rename(INTERMEDIARY_CODE = AGENT_CODE),
      gi_customer_details)

dim(customer_details_proc)
head(customer_details_proc)
```

## Add product details

```{r}
customer_details_complete <-
customer_details_proc %>% 
  left_join(account_info, by = "ACCOUNT_NO")

dim(customer_details_complete)
head(customer_details_complete)
```

Check: An Account Number is shared among different customers across the business lines.

```{r}
customer_details_complete %>% 
  count(ACCOUNT_NO, sort = TRUE)
```

```{r}
customer_details_complete %>% 
  filter(ACCOUNT_NO=="19702")
```


## Single column

```{r}
customer_details_final <-
customer_details_complete %>% 
  mutate(customer_details = glue("Agent Code:{INTERMEDIARY_CODE}
                                 Product Holding:{product_count}
                                 Current Product:{products}", 
                                 .na = "Not Found")) %>% 
  select(ACCOUNT_NO, ownership, intermediated, customer_details) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

dim(customer_details_final)
head(customer_details_final)
```
## Test

```{r}
customer_details_final %>% 
  filter(ACCOUNT_NO %in% c("10867","1610"))
```


## Merge with recommendation ratings

We add these details to the dataframe containing product recommendation ratings.

* Recommendations from the model
* Customer details containing intermediated and Account ownership information
* Product values

```{r}
ke_recommendations_df <- readRDS(file = "../../../../Models/KE/outputs/ratings/ke_recommendations_df.rds")

ke_recommendations_df
```


```{r}
ke_recommendations_detailed <-
ke_recommendations_df %>%
  left_join(customer_details_final, by = "ACCOUNT_NO") %>% 
  left_join(product_values, by = "PRODUCT") %>% 
  select(-accounts) %>% 
  relocate(customer_details, .after = everything())

dim(ke_recommendations_detailed)
head(ke_recommendations_detailed)
```

## Test

```{r}
ke_recommendations_detailed %>% 
  filter(ACCOUNT_NO %in% c("10867","1610")) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)
```

```{r}
unique(ke_recommendations_detailed$ownership)
```

# EXPORT

```{r}
# Detailed Recommendations
saveRDS(object = ke_recommendations_detailed, 
        file = "../outputs/ke_recommendations_detailed.rds")

saveRDS(object = product_values,
        file = "../outputs/product_values.rds")

getwd()
# Recommendations as a csv
# write_csv(x = ke_recommendations_detailed %>% select(-customer_details), 
#           file = "./recommendations_df.csv")

# Project image
save.image("./04May_Customer_details.RData")
load("./22Apr_Customer_details.RData")
```



