---
title: "Customer Details V2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PACKAGES

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(recommenderlab)
library(glue)
library(data.table)
library(dtplyr)
library(readxl)
library(tidyverse)
```

# OBJECTIVE

When hovering on a customer in the app, it should display whether a customer is intermediated (and agent code) and product details (number and name of products).

Extract the following details:
* Agent code tied to a customer
* Number of products held by a customer across the subsidiary and their names
* Business lines that owns the customer across the subsidiary
* Merge products held and agent code into a single column

# AGENT DETAILS

## General Insurance

```{r}
gi_products_1 <- read_xls(path = "../../../../../../Uganda/GI/policyheader_nonlife_uganda.xls", sheet = 1, col_types = "text")

gi_products_2 <- read_xls(path = "../../../../../../Uganda/GI/policyheader_nonlife_uganda.xls", sheet = 2, col_types = "text")

gi_products_3 <- read_xls(path = "../../../../../../Uganda/GI/policyheader_nonlife_uganda.xls", sheet = 3, col_types = "text")
```


```{r}
gi_products_raw <-
rbind(gi_products_1, gi_products_2, gi_products_3) %>% 
  as.data.table()

```

```{r}
gi_customers_raw <-
  gi_products_raw %>%
    filter (!is.na(ACCOUNT_NO)) %>%
    distinct (ACCOUNT_NO, INTERMEDIARY_CODE) %>%
    mutate (intermediated = if_else(!is.na(INTERMEDIARY_CODE), "Yes", "No")) %>%
    rename (AGENT_CODE = INTERMEDIARY_CODE) %>%
    as.data.table()

```

```{r}
gi_customers_raw
```

## Health Insurance

```{r}
health_customers_raw <-
fread(file = "../../../../../../Uganda/Health/ug_health_products_matched (2).csv") %>% 
  filter (!is.na(ACCOUNT_NO)) %>%
  mutate (INTERMEDIARY_CODE = na_if(INTERMEDIARY_CODE, "NULL")) %>%
  distinct (ACCOUNT_NO, INTERMEDIARY_CODE) %>%
  mutate (intermediated = if_else(!is.na(INTERMEDIARY_CODE), "Yes", "No")) %>%
  rename (AGENT_CODE = INTERMEDIARY_CODE) %>%
  as_tibble()
```


```{r}
customer_agents <- 
  rbind(gi_customers_raw, health_customers_raw) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE) %>%
  as_tibble()

customer_agents
```


# ACCOUNT INFO

Across the subsidiary

## Product count

```{r}
products_rating_matrix <-
readRDS("../../product_holding/products_rating_matrix.rds")

dim(products_rating_matrix)
```


```{r}
product_count <-
as(products_rating_matrix, "data.frame") %>% 
  select(user, item) %>% 
  count(user, name = "product_count") %>% 
  rename(ACCOUNT_NO = user)

product_count
```


## Customer products

```{r}
gc()

customer_products <-
as(products_rating_matrix, "data.frame") %>% 
  group_by(user) %>% 
  mutate(products = paste0(item, collapse = ", ")) %>% 
  distinct(user, .keep_all = TRUE) %>% 
  select(ACCOUNT_NO = user, products)

customer_products
```

## Ownership

Define business lines to which products belong to.

```{r}
health_products <-
readRDS("../../product_holding/health_product_holding_final.rds") %>% 
  distinct(PRODUCT = Product) %>%
  mutate(BUSINESS_LINE = "Health") %>%
  as_tibble()

gi_products <-
readRDS("../../product_holding/gi_product_holding_final.rds") %>% 
  distinct(PRODUCT = POLICY_TYPE) %>%
  mutate(BUSINESS_LINE = "General") %>%
  as_tibble()
```

```{r}
product_businesslines <-
rbind(health_products,
      gi_products) %>%
  as_tibble()

product_businesslines
```


```{r}
customer_ownership <-
as(products_rating_matrix, "data.frame") %>% 
  select(ACCOUNT_NO = user, PRODUCT = item) %>% 
  left_join(product_businesslines, by = "PRODUCT") %>% 
  group_by(ACCOUNT_NO) %>% 
  mutate(ownership = paste0(unique(BUSINESS_LINE), collapse = ", ")) %>% 
  select(ACCOUNT_NO, ownership) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

customer_ownership %>%
  ungroup() %>%
  count(ownership)
```

## Account info

```{r}
account_info <-
customer_products %>% 
  left_join(product_count, by = "ACCOUNT_NO") %>% 
  left_join(customer_ownership, by = "ACCOUNT_NO")

account_info
```

## Checks

```{r}
account_info %>% 
  ungroup() %>% 
  filter(str_detect(ownership,",")) %>% 
  count(ownership)
```

# CUSTOMER DETAILS

Merge account and agent information.

```{r}
rm(customer_details_final)

gc()

job::job({
customer_details_final <-
account_info %>% 
  left_join(customer_agents, by = "ACCOUNT_NO") %>% 
  mutate(customer_details = glue("Agent Code:{AGENT_CODE}
                                 Product Holding:{product_count}
                                 Current Products:{products}", 
                                 .na = "Not Found")) %>% 
  select(-AGENT_CODE,-product_count,-products) %>% 
  ungroup()
}, title = "Customer details")

gc()
```


```{r}
customer_details_final
```


# EXPORT

```{r}
# Detailed Recommendations
saveRDS(object = customer_details_final, 
        file = "../outputs/customer_details_final.rds")

#Product business lines
saveRDS(product_businesslines,"../outputs/product_businesslines.rds")

# Project image
save.image("../outputs/7June_Customer_details.RData")
```



