---
title: "Customer details"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# PACKAGES

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(recommenderlab)
library(glue)
library(data.table)
library(dtplyr)
library(readxl)
library(tidyverse)
```

# OBJECTIVE

When hovering on a customer in the app, it should display whether a customer is intermediated (and agent code) and product details (number and name of products).

Extract the following details:
* Agent code tied to a customer
* Number of products held by a customer across the subsidiary and their names
* Business lines that owns the customer across the subsidiary
* Merge products held and agent code into a single column

# AGENT DETAILS

## Asset Mgt

`ACCOUNT_NUMBER` is the unique customer identifier.

```{r}
asset_customers_raw <- read.csv(
  file = "../../../../../../C - Documentation/Data/festus_extraction/ZW/customer_investment.csv", 
  sep = ";", 
  na.strings = c(""," ")) %>% 
  filter(ACCOUNT_NUMBER > 10000) %>% 
  select(ACCOUNT_NO = ACCOUNT_NUMBER, AGENT_CODE) %>% 
  mutate(ACCOUNT_NO = as.character(ACCOUNT_NO)) %>% 
  mutate(intermediated = if_else(condition = is.na(AGENT_CODE), 
                                 true = "No", 
                                 false = "Yes"))

asset_customers_raw
```

## Life Insurance

`CUSTOMER_NUMBER` is the unique customer identifier.

```{r}
life_customers_raw <-
read.csv(file = "../../../../../../C - Documentation/Data/festus_extraction/ZW/customer_life_insurance.oipa.csv",
         sep = ";",
         na.strings = c("," )) %>% 
  filter(str_length(CUSTOMER_NUMBER) > 0) %>% 
  select(ACCOUNT_NO = CUSTOMER_NUMBER, AGENT_CODE) %>% 
  mutate(intermediated = if_else(condition = is.na(AGENT_CODE), 
                                 true = "No", 
                                 false = "Yes"))

life_customers_raw
```

## General Insurance

`CUSTOMER_NO` is the customer identifier.

```{r}
gi_customers_raw <-
read.csv(file = "../../../../../../C - Documentation/Data/festus_extraction/ZW/customer_general_insurance.csv") %>% 
  select(ACCOUNT_NO = CUSTOMER_NO,AGENT_CODE) %>% 
  mutate(intermediated = if_else(condition = is.na(AGENT_CODE), 
                                 true = "No", 
                                 false = "Yes"))

gi_customers_raw
```

## Lending

`account_no` is the customer identifier.

```{r}
lending_customers_raw <-
read_csv(file = "../../../../../../C - Documentation/Data/festus_extraction/ZW/customer_lending.csv") %>% 
  select(ACCOUNT_NO = account_no) %>% 
  mutate(AGENT_CODE = NA,
         intermediated = "No")

lending_customers_raw
```


## Customer agents

```{r}
customer_agents <-
rbind(asset_customers_raw,
      life_customers_raw,
      gi_customers_raw,
      lending_customers_raw) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

customer_agents
```


# ACCOUNT INFO

Across the subsidiary

## Product count

```{r}
products_rating_matrix <-
readRDS(file = "../../02. Create rating matrices/outputs/products_rating_matrix.rds")

dim(products_rating_matrix)
```


```{r}
product_count <-
as(products_rating_matrix, "data.frame") %>% 
  select(user, item) %>% 
  count(user, name = "product_count") %>% 
  rename(ACCOUNT_NO = user)

product_count
```


## Customer products

```{r}
gc()

customer_products <-
as(products_rating_matrix, "data.frame") %>% 
  group_by(user) %>% 
  mutate(products = paste0(item, collapse = ", ")) %>% 
  distinct(user, .keep_all = TRUE) %>% 
  select(ACCOUNT_NO = user, products)

customer_products
```

## Ownership

Define business lines to which products belong to.

```{r}
asset_products <-
readRDS(file = "../../01. Determine product holding/outputs/objects/asset_product_holding.rds") %>% 
  distinct(PRODUCT) %>%
  mutate(BUSINESS_LINE = "Asset")

life_products <-
readRDS(file = "../../01. Determine product holding/outputs/objects/life_product_holding.rds") %>% 
  distinct(PRODUCT) %>%
  mutate(BUSINESS_LINE = "Life")

gi_products <-
readRDS(file = "../../01. Determine product holding/outputs/objects/gi_product_holding.rds") %>% 
  select(PRODUCT = DESCRIPTION) %>% 
  distinct(PRODUCT) %>%
  mutate(BUSINESS_LINE = "General")

lending_products <-
readRDS(file = "../../01. Determine product holding/outputs/objects/lending_product_holding.rds") %>% 
  select(PRODUCT = product) %>% 
  distinct(PRODUCT) %>%
  mutate(BUSINESS_LINE = "Lending")
```


```{r}
product_businesslines <-
rbind(asset_products,
      life_products,
      gi_products,
      lending_products)

product_businesslines
```


```{r}
customer_ownership <-
as(products_rating_matrix, "data.frame") %>% 
  select(ACCOUNT_NO = user, PRODUCT = item) %>% 
  left_join(product_businesslines, by = "PRODUCT") %>% 
  group_by(ACCOUNT_NO) %>% 
  mutate(ownership = paste0(unique(BUSINESS_LINE), collapse = ", ")) %>% 
  select(ACCOUNT_NO, ownership) %>% 
  distinct(ACCOUNT_NO, .keep_all = TRUE)

customer_ownership
```

## Account info

```{r}
account_info <-
customer_products %>% 
  left_join(product_count, by = "ACCOUNT_NO") %>% 
  left_join(customer_ownership, by = "ACCOUNT_NO")

account_info
```

## Checks

```{r}
account_info %>% 
  ungroup() %>% 
  filter(str_detect(ownership,",")) %>% 
  count(ownership)
```

# CUSTOMER DETAILS

Merge account and agent information.

```{r}
rm(customer_details_final)

gc()

job::job({
customer_details_final <-
account_info %>% 
  left_join(customer_agents, by = "ACCOUNT_NO") %>% 
  mutate(customer_details = glue("Agent Code:{AGENT_CODE}
                                 Product Holding:{product_count}
                                 Current Products:{products}", 
                                 .na = "Not Found")) %>% 
  select(-AGENT_CODE,-product_count,-products) %>% 
  ungroup()
}, title = "Customer details")

gc()
```


```{r}
customer_details_final
```


# EXPORT

```{r}
# Detailed Recommendations
saveRDS(object = customer_details_final, 
        file = "../outputs/customer_details_final.rds")

#Product business lines
saveRDS(product_businesslines,"../outputs/product_businesslines.rds")


# Project image
save.image("../outputs/19May_Customer_details.RData")
```



