---
title: "ZW APIs"
author: "John Mwangi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ABOUT

This is the main file for creating, documenting, and testing the development process of the APIs.

# Packages

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(httr)
library(jsonlite)
library(recommenderlab)
library(DBI)
library(RSQLite)
library(tidyverse)
```

# Required objects

```{r}
ng_rec_model <- readRDS(file = "../../../App/uap_cross_sell/objects/models/Nigeria.rds")
```

# Database connections

```{r}
ng_sqlite_path <- "../../../App/uap_cross_sell/db/ng_cs.db"
con_ng <- dbConnect(drv = SQLite(), ng_sqlite_path)
```

# Constants

```{r}
ROUND_OFF <- 3
```

# Scenario 1

Where the Account Number is provided, the model returns:
* Product recommendations for the customer
* Ratings for the various products

Returns:
* dataframe converted to json

Additional information (same columns that are on the tool):
* Business line of the product
* Max rating among the products
* Customer ownership
* Whether the customer is intermediated or not
* Product value of the recommended product
* Additional customer details: product holding, products held, account numbers per business line

## Create a function

```{r}
predict_on_accounts <- function(account_num, recomm_limit){
  
  account_num <- str_remove_all(string = account_num, pattern = " ")
  records <- strsplit(x = account_num, split = ",")[[1]]
  
  chosen_customers <-
    tbl(src = con_ng, "recommendations_detailed") %>% 
    filter(ACCOUNT_NO %in% records) %>%
    group_by(ACCOUNT_NO, BUSINESS_LINE) %>% 
    arrange(desc(rating)) %>% 
    collect() %>% 
    slice(1:recomm_limit) %>% 
    arrange(desc(max_rating)) %>% 
    mutate(max_rating = round(max_rating, ROUND_OFF),
           rating = round(rating, ROUND_OFF))
  
  return(chosen_customers)
}
```

## Test the function

```{r}
predict_on_accounts(account_num = "3013460492,3013483433", recomm_limit = 3)
```

## Create API

Refer to `predict_on_accounts_api.R` When run, this will return a json file.

## Test API results

View json file in tabular format.

```{r}
fromJSON(txt = "../outputs/response_scenario1.json")
```

## Run API

Refer to `run_predict_on_accounts.R` This will prevent the API's port from changing and allow it to be ran as a background job.

Run `run_predict_on_accounts.R` as a job.

## Call the API

Send a http call to the API. The request to this call should have status 200.

```{r}
base_url <- "http://127.0.0.1:6208/predict-on-accounts"

params <- list(account_num = "3013460492,3013483433", recomm_limit = 3)

query_url <- modify_url(url = base_url, query = params)

request <- GET(url = query_url)

response <- content(x = request, as = "text", encoding = "utf-8")

fromJSON(txt = response)
```

Convert call to a function.

```{r}
api_call_1 <- function(account_num, recomm_limit){
  
  base_url <- "http://127.0.0.1:6208/predict-on-accounts"
  
  params <- list(account_num = account_num, recomm_limit = recomm_limit)
  
  query_url <- modify_url(url = base_url, query = params)
  
  request <- GET(url = query_url)
  
  response <- content(x = request, as = "text", encoding = "utf-8")
  
  fromJSON(txt = response)
}
```


```{r}
api_call_1(account_num = "3013460492,3013483433", recomm_limit = 3)
```

# Scenario 2

## Create a function

The function returns a list of prospective customers based on selected user criteria.

```{r}
fetch_top_customers <- function(ownership, intermediated, min_value, max_value, recomm_limit){
  
top_customers <-
tbl(src = con_ng, "recommendations_detailed") %>%
  group_by(ACCOUNT_NO, BUSINESS_LINE) %>% 
  filter(intermediated == !!intermediated) %>% 
  filter(ownership == !!ownership) %>% 
  filter(product_value >= min_value) %>% 
  filter(product_value <= max_value) %>% 
  collect() %>% 
  slice(1:recomm_limit)

return(top_customers)
}
```

## Test the function.

```{r}
fetch_top_customers(ownership = "General", 
                    intermediated = "No", 
                    min_value = 0000, 
                    max_value = 200000, 
                    recomm_limit = 3)
```

## Create API

Refer to `fetch_top_customers.R` When run, this will return a json file.

## Test API results

View json file in tabular format.

```{r}
fromJSON(txt = "../outputs/response_scenario2.json")
```

## Run API

Refer to `run_fetch_top_customers.R` This will prevent the API's port from changing and allow it to be ran as a background job.

Run `run_fetch_top_customers.R` as a job.

## Call the API

Send a http call to the API. The request to this call should have status 200.

```{r}
base_url <- "http://127.0.0.1:6209/fetch-top-customers"

params <- list(ownership = "General", 
               intermediated = "No", 
               min_value = 50000, 
               max_value = 200000, 
               recomm_limit = 3)

query_url <- modify_url(url = base_url, query = params)

request <- GET(url = query_url)

response <- content(x = request, as = "text", encoding = "utf-8")

fromJSON(txt = response)
```

Convert call to a function.

```{r}
api_call_2 <- function(ownership, intermediated, min_value, max_value, recomm_limit){
  
  base_url <- "http://127.0.0.1:6208/fetch-top-customers"
  
  params <- list(ownership = ownership, 
                 intermediated = intermediated, 
                 min_value = min_value, 
                 max_value = max_value, 
                 recomm_limit = recomm_limit)
  
  query_url <- modify_url(url = base_url, query = params)
  
  request <- GET(url = query_url)
  
  response <- content(x = request, as = "text", encoding = "utf-8")
  
  fromJSON(txt = response)
}
```


```{r}
api_call_2(ownership = "General", 
           intermediated = "No", 
           min_value = 50000, 
           max_value = 200000, 
           recomm_limit = 3)
```

# Scenario 3

Include additional products on top of what one has purchased.

## Create a function


```{r}
supp_sqlite_path <- "../../../App/uap_cross_sell/db/support.db"
con_supp <- dbConnect(drv = SQLite(), supp_sqlite_path)
```



```{r}
predict_on_choices <- function(user_choices, recomm_limit){
    
    #Products not selected
    not_user_choices <-
      tbl(src = con_supp, "support") %>% 
      filter(country=="Nigeria") %>% 
      filter(!products %in% user_choices & !is.na(products)) %>%
      collect() %>% 
      pull(products)
    
    
    #Convert to a table
    choices <- 
      tibble(choice = rep(x = c(1,0), 
                          times = c(length(user_choices), 
                                    length(not_user_choices))
      ))
    
    user_choices_df <-
      choices %>% 
      mutate(user_choices = c(user_choices, not_user_choices)) %>% 
      distinct(user_choices, .keep_all = TRUE)
    
    #Convert to wide format
    user_choices_df <- 
      pivot_wider(data = user_choices_df,
                  names_from = user_choices, 
                  values_from = choice)
    
    #Convert to binaryRatingMatrix
    user_choices_mat <- as.matrix(user_choices_df)
    user_choices_ratmat <- as(user_choices_mat,"binaryRatingMatrix")
    
    #Predict using model
    user_choice_recommendations <-
      tryCatch(expr = predict(object = ng_rec_model, 
                      newdata = user_choices_ratmat, 
                      type="ratings"),
               error = function(e){
                 stop("Ensure the products specified match the selected country.")
               })
    
    #Convert prediction to dataframe
    user_choice_recommendations_df <-
      as(user_choice_recommendations, "data.frame") %>% 
      rename(PRODUCT = item) %>%
      left_join(tbl(src = con_ng, "product_businesslines"),
                by = "PRODUCT", 
                copy = TRUE) %>% 
      left_join(tbl(src = con_ng, "product_values"),
                by = "PRODUCT",
                copy = TRUE) %>% 
      relocate(BUSINESS_LINE, .after = PRODUCT) %>% 
      group_by(BUSINESS_LINE) %>% 
      arrange(desc(rating), .by_group = TRUE) %>% 
      slice(1:recomm_limit) %>% 
      select(-accounts) %>% 
      mutate(rating = round(rating, ROUND_OFF))
    
    return(user_choice_recommendations_df)
}
```

## Test the function

```{r}
predict_on_choices(user_choices = "Goods in transit", recomm_limit = 3)
```

## Create API

Refer to `predict_on_choices_api.R` When run, this will return a json file.

## Test API results

View json file in tabular format.

```{r}
fromJSON(txt = "../outputs/response_scenario3.json")
```

## Run API

Refer to `run_predict_on_choices.R` This will prevent the API's port from changing and allow it to be ran as a background job.

Run `run_predict_on_choices.R` as a job.

## Call the API

Send a http call to the API. The request to this call should have status 200.

```{r}
base_url <- "http://127.0.0.1:6211/predict-on-choices"

params <- list(user_choices = "Goods in transit", recomm_limit = 3)

query_url <- modify_url(url = base_url, query = params)

request <- GET(url = query_url)

response <- content(x = request, as = "text", encoding = "utf-8")

fromJSON(txt = response)
```

Convert call to a function.

```{r}
api_call_3 <- function(user_choices, recomm_limit){
  
  base_url <- "http://127.0.0.1:6211/predict-on-choices"
  
  params <- list(user_choices = "Goods in transit", recomm_limit = 3)
  
  query_url <- modify_url(url = base_url, query = params)
  
  request <- GET(url = query_url)
  
  response <- content(x = request, as = "text", encoding = "utf-8")
  
  fromJSON(txt = response)
}
```


```{r}
api_call_3(user_choices = "Goods in transit", recomm_limit = 3)
```


# Scenario 4

Popular products

## Create a function

```{r}
fetch_popular_products <- function(recomm_limit){

popular_products <-
    left_join(x = tbl(src = con_ng, "popular_products"),
              y = tbl(src = con_ng, "product_values"),
              by = "PRODUCT") %>% 
      group_by(BUSINESS_LINE) %>% 
      collect() %>% 
      slice(1:recomm_limit) %>% 
      rename(PURCHASES = n) %>% 
      select(-accounts)

return(popular_products)
}
```

## Test the function

```{r}
fetch_popular_products(recomm_limit = 4)
```

## Create API

Refer to `fetch_popular_products_api.R` When run, this will return a json file.

## Test API results

View json file in tabular format.

```{r}
fromJSON(txt = "../outputs/response_scenario1.json")
```

## Run API

Refer to `run_predict_on_accounts.R` This will prevent the API's port from changing and allow it to be ran as a background job.

Run `run_predict_on_accounts.R` as a job.

## Call the API

Send a http call to the API. The request to this call should have status 200.

```{r}
base_url <- "http://127.0.0.1:6210/fetch-popular-products"

params <- list(recomm_limit = 4)

query_url <- modify_url(url = base_url, query = params)

request <- GET(url = query_url)

response <- content(x = request, as = "text", encoding = "utf-8")

fromJSON(txt = response)
```

Convert call to a function.

```{r}
api_call_4 <- function(recomm_limit){
  
  base_url <- "http://127.0.0.1:6208/fetch-popular-products"
  
  params <- list(recomm_limit = recomm_limit)
  
  query_url <- modify_url(url = base_url, query = params)
  
  request <- GET(url = query_url)
  
  response <- content(x = request, as = "text", encoding = "utf-8")
  
  fromJSON(txt = response)
}
```


```{r}
api_call_4(recomm_limit = 4)
```

