---
title: "Support tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# ORIGINAL TABLE

This table will hold information that cuts across all countries. It will be used for dynamically updating UI elements of the tool. 

This table will contain, for each country:
* Products under each country
* Ownership of customers

## Packages

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(DBI)
library(tidyverse)
```


## Ownership information

```{r}
ke_ownership <- readRDS(file = "../../../Data Prep/KE/03. Extract additional customer details/outputs/ke_recommendations_detailed.rds") %>%
  ungroup() %>%
  distinct(ownership) %>%
  pull(ownership)

zw_ownership <- readRDS(file = "../outputs/zw_recommendations_detailed.rds") %>%
  ungroup() %>%
  distinct(ownership) %>%
  pull(ownership)

ke_ownership
zw_ownership
```


```{r}
supp_sqlite_path_ug <- "../../../App/uap_cross_sell/db/support.db"
con_supp_ug <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path_ug)

ug_ownership <-
tbl(src = con_supp_ug, "support") %>% 
  filter(country=="Uganda") %>% 
  filter(!is.na(ownership)) %>% 
  pull(ownership)

ug_ownership
```


## Product information

```{r}
ke_products <- readRDS(file = "../../../Data Prep/KE/02. Create rating matrices/outputs/products_rating_matrix.rds") %>%
  colnames()

zw_products <- readRDS(file = "../../../Data Prep/ZW/02. Create rating matrices/outputs/products_rating_matrix.rds") %>%
  colnames()

length(ke_products)
length(zw_products)
```

## Tables

```{r}
support_df <-
rbind(
  tibble(
    country = "Zimbabwe",
    products = zw_products,
    ownership = c(zw_ownership,
                  rep(NA, times = length(zw_products) - length(zw_ownership))
                  )
    ),
  
  tibble(
    country = "Kenya",
    products = ke_products,
    ownership = c(ke_ownership,
                  rep(NA, times = length(ke_products) - length(ke_ownership))
                  )
    )
  )

support_df
```

## Establish db connection

```{r}
supp_sqlite_path <- "../../../App/uap_cross_sell/db/support.db"
con_supp <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path)


```


## Save to db

```{r}
copy_to(dest = con_supp, 
        df = support_df, 
        name = "support", 
        overwrite = TRUE, 
        temporary = FALSE)
```

# UPDATES

## Countries in db

```{r}
dbListTables(conn = con_supp)
```

```{r}
tbl(src = con_supp, "support") %>% 
  distinct(country)
```


## Remove outdated info

### Zimbabwe

```{r}
support_df <-
tbl(src = con_supp, "support") %>% 
  filter(country != "Zimbabwe") %>% 
  collect()

support_df
```


### Ghana

Compare the two databases.

```{r}
supp_sqlite_path_gh <- "../../../App/uap_cross_sell/db/support_tayo.db"
con_supp_gh <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path_gh)

dbListTables(conn = con_supp_gh)
```


```{r}
tbl(src = con_supp_gh, "support") %>% 
  collect() %>% 
  summarise(across(.cols = everything(), 
                   .fns = ~length(unique(.))))


tbl(src = con_supp_gh, "support") %>% 
  distinct(country)


tbl(src = con_supp_gh, "support") %>% 
  filter(country=="Ghana")
```


```{r}
tbl(src = con_supp, "support") %>% 
  collect() %>% 
  summarise(across(.cols = everything(), 
                   .fns = ~length(unique(.))))

tbl(src = con_supp, "support") %>% 
  distinct(country)
```

Remove outdated information

```{r}
support_df <-
tbl(src = con_supp, "support") %>% 
  filter(country != "Ghana") %>% 
  collect()

support_df
```

Extract up-to-date information.

```{r}
support_gh <-
tbl(src = con_supp_gh, "support") %>% 
  filter(country=="Ghana") %>% 
  collect()

support_gh
```

Merge the two dataframes.

```{r}
support_tbl <- rbind(support_df, support_gh)

support_tbl
```


## Ownership

### Nigeria

```{r}
path_ng <- "../../../App/uap_cross_sell/db/ng_cs.db"
con_ng <- dbConnect(drv = RSQLite::SQLite(), path_ng)
dbListTables(conn = con_ng)

ng_ownership <- tbl(src = con_ng, "recommendations_detailed") %>% 
  distinct(ownership) %>% 
  pull(ownership)

ng_ownership
```


### Uganda

```{r}
ug_ownership <- readRDS(file = "../../UG/outputs/ug_recommendations_detailed.rds") %>% 
  ungroup() %>% 
  distinct(ownership) %>% 
  pull(ownership)
```


### Zimbabwe

```{r}
zw_ownership
```

## Products

### Uganda

```{r}
ug_products <- readRDS(file = "../../../Data Prep/UG/product_holding/products_rating_matrix.rds") %>% 
  colnames()
```

### Zimbabwe

```{r}
zw_products
```


## Table

Uganda.

```{r}
ug_tibble <- tibble(
    country = "Uganda",
    products = ug_products,
    ownership = c(ug_ownership,
                  rep(NA, times = length(ug_products) - length(ug_ownership))
                  )
    )

ug_tibble
```

Zimbabwe.
```{r}
zw_tibble <- tibble(
    country = "Zimbabwe",
    products = zw_products,
    ownership = c(zw_ownership,
                  rep(NA, times = length(zw_products) - length(zw_ownership))
                  )
    )

zw_tibble
```


## Update db

```{r}
copy_to(dest = con_supp, 
        df = support_df, 
        name = "support", 
        overwrite = TRUE, 
        temporary = FALSE)
```

Uganda.

```{r}
dbWriteTable(con = con_supp, "support", ug_tibble, append=TRUE, row.names = FALSE)
```

Zimbabwe.

```{r}
dbWriteTable(conn = con_supp, 
             name = "support", 
             value = zw_tibble, 
             append=TRUE, 
             row.names = FALSE)
```


Ghana.

```{r}
copy_to(dest = con_supp,
        df = support_tbl, 
        name = "support", 
        overwrite = TRUE, 
        temporary = FALSE)
```


# Sense check


```{r}
tbl(src = con_supp, "support") %>% 
  filter(country %in% c("Zimbabwe","Kenya")) %>% 
  collect() %>% 
  dim()
  
  
tbl(src = con_supp, "support") %>% 
  filter(country=="Uganda") %>% 
  collect() %>% 
  dim()

dim(zw_tibble)

tbl(src = con_supp, "support") %>% 
  filter(country=="Zimbabwe") %>% 
  collect() %>% 
  dim()

tbl(src = con_supp, "support") %>% 
  distinct(country)

tbl(src = con_supp, "support") %>% 
  collect() %>% 
  summarise_all(~length(unique(.)))
```



