---
title: "Support tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# SUPPORT TABLE

*Additional tables will be appended instead. Refer go to: Update table*

This table will hold information that cuts across all countries. It will be used for dynamically updating UI elements of the tool. 

This table will contain, for each country:
* Products under each country
* Ownership of customers

## Packages

```{r message=FALSE, warning=FALSE}
rm(list = ls())

library(DBI)
library(tidyverse)
```

## db Connection

```{r}
supp_sqlite_path <- "../../../App/uap_cross_sell/db/support.db"

con_supp <- dbConnect(drv = RSQLite::SQLite(), supp_sqlite_path)

dbListTables(conn = con_supp)
```

## SD Update

### Product information

```{r}
sd_products <-
readRDS(file = "../../../Data Prep/SD/03. Create rating matrices/outputs/products_rating_matrix.rds") %>% 
  colnames()

sd_products
```

### Ownership information

```{r}
sd_ownership <-
readRDS(file = "../outputs/sd_recommendations_detailed.rds") %>% 
  ungroup() %>% 
  distinct(ownership) %>% 
  pull(ownership)

sd_ownership
```

### Dataframe

```{r}
sd_tibble <-
tibble(country = "Sudan",
       products = sd_products,
       ownership =c(sd_ownership, 
                    rep(x = NA, 
                        times = length(sd_products) - length(sd_ownership))
                    )
       )

sd_tibble
```

## Save to db

```{r}
dbWriteTable(con = con_supp, "support", sd_tibble, append=TRUE, row.names = FALSE)
```


# Sense check

```{r}
dbListTables(conn = con_supp)

dim(sd_tibble)

tbl(src = con_supp, "support") %>% 
  filter(country=="Sudan") %>% 
  collect() %>% 
  dim()
```

